\documentclass[letterpaper,12pt,dvips]{article}
\usepackage[textwidth=6.5in,textheight=9in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{color}
\usepackage{vector}
\usepackage{graphicx}     % From LaTeX distribution
%\usepackage{subfigure}    % From CTAN/macros/latex/contrib/supported/subfigure
\usepackage{pst-all}      % From PSTricks
\usepackage{pst-poly}     % From pstricks/contrib/pst-poly
\usepackage{multido}      % From PSTricks
\usepackage[center,footnotesize]{caption}

\numberwithin{equation}{section}

\begin{document}

\title{Pre-processor and Pre-Post-Processor for NASA 2D CESE code}
\author{Yung-Yu Chen}
\date{2008.12.2}

\maketitle

\tableofcontents
%\listoffigures

\hspace{.5cm}

\section{NASA 2D CESE Code}

\section{Pre/Pre-Post-Processing}

MESHED version 0.0.1 (mercurial revision id: \verb+7e8ef5002a8b+).

\begin{thebibliography}{99}
\bibitem{b:chang95} Chang, S.-C. (1995), 
``The Method of Space-Time Conservation Element and Solution Element -- 
A New Approach for Solving the Navier-Stokes and Euler Equation.''
Journal of Computational Physics 119(2): 295-324.
\bibitem{b:chang02} Chang, S.-C. (2002, July),
``Courant number insensitive ce/se schemes.'' AIAA Paper 2002-3890.
\bibitem{b:chang03} Chang, S.-C. and Wang, X.-Y. (2003), 
``Multi-dimensional courant number insensitive ce/se euler solvers for 
applications involving highly nonuniform meshes,'' 
AIAA Paper 2003-5285.
\bibitem{b:chang05} Chang, S.-C., Wu, Y., Yang, V., and Wang, X.-Y., 
``Local time-stepping procedures for the space-time conservation element 
and solution element method,'' 
International Journal of Computational Fluid Dynamics, 
vol. 19, no. 5, pp. 359-380, July 2005.
\bibitem{b:chang08} Chang, S.-C., not yet published script.
\bibitem{b:Python} \url{http://www.python.org/}.
\end{thebibliography}

\end{document}
